---
title: "Task 2 - Cake ingredients"
author: "Chris Proudfoot"
date: "22/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning=FALSE,message=FALSE}
library(tidyverse)
library(here)
cake_ingredients <- read_csv(here("clean_data/cake_ingredients_clean.csv"))
```


### 1. Which cake has the most cocoa in it?


```{r}
most_cocoa <- cake_ingredients %>%
  filter(ingredient == "cocoa") %>%
  arrange(desc(amount)) %>%
  head(1)

most_cocoa
```
Here I filtered out any cake with cocoa as an ingredient then arranged them in descending order from highest to lowest. I then took the top cake which was one bowl chocolate.


### 2. For sponge cake, how many cups of ingredients are used in total?


```{r}
cups_in_sponge <- cake_ingredients %>%
  filter(cake == "sponge",
         measure == "cup") %>%
  summarise(amount_of_cups = sum(amount))

cups_in_sponge
```



### 3. How many ingredients are measured in teaspoons?


```{r}
ingredients_in_tsp <- cake_ingredients %>%
  select(ingredient, measure) %>%
  group_by(measure) %>%
  distinct(ingredient) %>%
  filter(measure == "teaspoon") %>%
  count(measure)

ingredients_in_tsp
```
Here by grouping by the measurements and using the distinct function which returns one of each unique item in ingredient I was able to find out which ingredient use which unit of measurement. I then used the count function to return to total amount of ingredients that use the teaspoon as a measurement.

NOTE. Sour creams measurement field is NA and it's measurement cup is attached to the ingredient name 'sour cream cup'. this did not affect answering the questions asked so I decided to leave it as is.


### 4. Which cake has the most unique ingredients?

```{r}
unique_ingredients <- cake_ingredients %>%
  group_by(cake) %>%
  summarise(num_ingredients = n()) %>%
  arrange(desc(num_ingredients))

unique_ingredients
```
As the dataset is essentially a list of ingredients, I used the summarise function to count how many times each cake appeared in the list. It was a drew for the most ingredient with babas au rhum and one bowl chocolate.


### 5. Which ingredients are used only once?

```{r}
one_use_ingredients <- cake_ingredients %>%
  group_by(ingredient) %>%
  filter(n() == 1) %>%
  select(ingredient)

one_use_ingredients
```
Here I grouped everything by ingredients and then return only the groups of one. 
