---
title: "Task 4 - Halloween Candy Data"
author: "Chris Proudfoot"
date: "24/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning=FALSE,message=FALSE}
library(tidyverse)
library(here)
library(lubridate)
```

```{r}
candy <- read_csv(here("clean_data/boing_candy_clean.csv"), col_types = cols(gender = col_character(), country = col_character()))
```

### 1. What is the total number of candy ratings given across the three years. (number of candy ratings, not number of raters. Don’t count missing values)


```{r}
number_of_ratings <- nrow(candy)

number_of_ratings  
```
The ratings only contains ratings(no NAs) so I counted the number of rows which returned 222214.


### 2. What was the average age of people who are going out trick or treating and the average age of people not going trick or treating?


```{r}
average_age <- candy %>%
  filter(!is.na(going_trick_or_treating), !is.na(age)) %>%
  group_by(going_trick_or_treating) %>%
  summarise(mean_age = mean(age)
            )
average_age
```
First I had to remove any NA values from both the age and going_trick_or_treating columns. Then I gouped them by who was going and who was not. Finally I summerised these by the mean of the age column,


### 3. For each of joy, despair and meh, which candy bar revived the most of these ratings?


```{r}
candy_ratings_totalled <- candy %>%
  group_by(rating, candy) %>%
  summarise(count_rating = n()) %>%
  filter(count_rating == max(count_rating))


candy_ratings_totalled
```


4. How many people rated Starburst as despair?


```{r}
dispair_starburst <- candy %>%
  filter(candy == "starburst", rating == "DESPAIR") %>%
  group_by(candy) %>%
  summarise(rating = n())

dispair_starburst
  
```


```{r}
candy_rating_points <- candy %>%
  mutate(rating_points =
           case_when(str_detect(rating, "DESPAIR") ~ -1,
                     str_detect(rating, "JOY") ~ 1,
                     str_detect(rating, "MEH") ~ 0
                     )
         )

candy_rating_points
```

```{r}
candy_rating_points %>%
  group_by(gender, candy) %>%
  summarise(total_points = sum(rating_points)) %>%
  group_by(gender) %>% 
  filter(total_points == max(total_points))
```

Most popular candy in each year

```{r}
candy_rating_points %>%
  mutate(timestamp = year(timestamp)) %>%
  group_by(timestamp, candy) %>%
  summarise(total_points = sum(rating_points)) %>%
  filter(total_points == max(total_points))
```

```{r}
candy_rating_points %>% 
  mutate(country = case_when(!country %in% c(
    "United Kingdom", "Canada", "United States", NA) ~ "All other countries",
    TRUE ~ country)) %>% 
  group_by(country, candy) %>% 
  summarise(total_points = sum(rating_points)) %>% 
  group_by(country) %>%
  filter(total_points == max(total_points))
```

