---
title: "Task 4 - Halloween Candy Data"
author: "Chris Proudfoot"
date: "24/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning=FALSE,message=FALSE}
library(tidyverse)
library(here)
candy <- read_csv(here("clean_data/boing_candy_clean.csv"))
```


### 1. What is the total number of candy ratings given across the three years. (number of candy ratings, not number of raters. Don’t count missing values)


```{r}
number_of_ratings <- nrow(candy)

number_of_ratings  
```
The ratings only contains ratings(no NAs) so I counted the number of rows which returned 222214.


### 4. What was the average age of people who are going out trick or treating and the average age of people 3. not going trick or treating?


```{r}
average_age <- candy %>%
  filter(!is.na(going_trick_or_treating), !is.na(age)) %>%
  group_by(going_trick_or_treating) %>%
  summarise(mean_age = mean(age)
            )
average_age
```
First I had to remove any NA values from both the age and going_trick_or_treating columns. Then I gouped them by who was going and who was not. Finally I summerised these by the mean of the age column,


### 3. For each of joy, despair and meh, which candy bar revived the most of these ratings?


```{r}
candy_ratings_totalled <- candy %>%
  group_by(rating, candy) %>%
  summarise(count_rating = n()) %>%
  filter(count_rating == max(count_rating))


candy_ratings_totalled
```


```{r}
# dispair_starburst <- candy %>%
  
```

